Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-08-28 manuscript.tex
overleaf update

>>>>

\textcolor{red}{ The following is very rough, taken from years ago when I first started writing the manuscript }
This study aimed to evaluate the feasibility of transmitting high clock-rate pulse position modulated (PPM) data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD). The investigation was driven by recent advancements in NbN SNSPDs, which have achieved a jitter as low as 50 ps at the FW(1/100)M level, enabling the demonstration of PPM with 50 ps slot widths and a 20 GHz clock. The aim was to increase the data rate by a factor of 10, from 2 GHz to 20 GHz, in the next generation of the Deep Space Optical Communication (DSOC) project.
